A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2013-10-27 jacobian_calc_CMAME.tex
Fix author block

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%%\usepackage{graphics}
%% or use the graphicx package for more complicated commands
%%\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}
%%\usepackage{color}
%%\usepackage{tkz-base}
\usepackage{pgfplots}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
\author{Michael D. Brothers}
\author{John T. Foster\corref{cor1}}
\cortext[cor1]{Corresponding Author: john.foster@utsa.edu}
\author{Harry R. Millwater}
\address{Mechanical Engineering Department, The University of Texas at San Antonio}

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Newton's method \sep Newton-Raphson \sep numeric differentiation \sep complex-step \sep finite-difference \sep automatic-differentiation \sep Jacobian \sep tangent-stiffness
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC [2010] 65D25 
\end{keyword}

@@

The methods were compared by running two sets of test problems where each method would solve a
problem concurrently. Each test problem simulated a $4$ by $.25$ by $.25$ meter block of metal
undergoing tension along the axis parallel to the long dimension of the block. The test problems
were set up in \emph{Perdigm} as quasistatic equillibrium problems, where the displacement boundary
conditions used to apply tension were applied gradually, in 'load steps', and an equilibrium
solution for each load step was achieved before applying the next load step. The purpose of applying
the load in gradual steps is a widely used technique to ensure the Newton-Raphson method is always
guessing near the actual solution. The material properties of the model were set at $8.0E-9$ $ metric
tonne/ mm^3$ density, $1.515E4$ $MPa$ bulk modulus, and $7.813E4$ $MPa$ shear modulus. The peridynamic
horizon used in a test problem was three times the node spacing for the corrisponding model mesh.
This value for horizon was chosen out of experience to insure that every node could have at least
one nonlocal connection along the diagonal of the node grid.

>>>>

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%%\usepackage{graphics}
%% or use the graphicx package for more complicated commands
%%\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}
%%\usepackage{color}
%%\usepackage{tkz-base}
\usepackage{pgfplots}
\usepackage{siunitx}

@@

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
\author{Michael D. Brothers}
\author{John T. Foster\corref{cor1}}
\ead{john.foster@utsa.edu}
\cortext[cor1]{Corresponding Author}

\author{Harry R. Millwater\corref{}}
\address{Mechanical Engineering Department, The University of Texas at San Antonio}

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Newton's method \sep Newton-Raphson \sep numeric differentiation \sep complex-step \sep finite-difference \sep automatic-differentiation \sep Jacobian \sep tangent-stiffness
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC [2010] 65D25 
\end{keyword}

@@

The methods were compared by running two sets of test problems where each method would solve a problem concurrently. Each test problem simulated a $\SI{4}{\meter}$ by $\SI{0.25}{\meter}$ by $\SI{0.25}{\meter}$ meter block of a material undergoing tension along the axis parallel to the long dimension of the block. The test problems were set up in \emph{Perdigm} as quasistatic equillibrium problems, where the displacement boundary conditions used to apply tension were applied gradually, in `load steps', and an equilibrium solution for each load step was achieved before applying the next load step. The purpose of applying the load in gradual steps is a widely used technique to ensure the Newton's method is always initialized near the actual solution and therefore likely to converge. The material properties of the model were meant to replicate a typical metal and had values of $\SI{1.515e4}{\mega\pascal}$ for bulk modulus, and $\SI{7.813e4}{\mega\pascal}$ for shear modulus. The peridynamic horizon, a length scale that effectively sets the bandwidth of tangent-stiffness in the computation, used in the test problems was always set to three times the nominal discretization size (i.e. node spacing in the particle discretiztion scheme). This results in a minimum tangent-stiffness matrix bandwidth of 7 (for an opitimal node numbering scheme).
